BioTime

### 2020-09-08 data-raw/biotime.Rmd
Get rid of duplicates from synonym scientific names matching to the same ID.

biotime_data <- biotime_ids %>%
  select(id = acceptedNameUsageID,input, scientificName) %>%
  distinct() %>%
  right_join(data, by = c("input" = "genus_species")) %>%
  rename(sourceName = input)
```

>>>>

biotime_data <- biotime_ids %>%
  select(id = acceptedNameUsageID,input) %>%
  distinct() %>%
  right_join(data, by = c("input" = "genus_species")) %>%
  rename(sourceName = input) %>%
  mutate(scientificName = taxadb::get_names(id))
```
